


\begin{document}


\begin{minted}{text}
  stud@sysrescue:~/projects/webapp$ dub run --compiler=ldc2
    Starting Performing "debug" build using ldc2 for x86_64.
  Up-to-date hunt 1.7.17: target for configuration [library] is up to date.
  Up-to-date hunt-extra 1.2.3: target for configuration [library] is up to date.
  Up-to-date hunt-net 0.7.1: target for configuration [default] is up to date.
  Up-to-date hunt-http 0.8.2: target for configuration [default] is up to date.
  Up-to-date protobuf 0.6.2: target for configuration [protobuf] is up to date.
  Up-to-date grpc 0.5.0-beta.2: target for configuration [library] is up to date.
  Up-to-date hunt-redis 1.4.1: target for configuration [library] is up to date.
  Up-to-date hunt-cache 0.10.1: target for configuration [library] is up to date.
  Up-to-date hunt-console 0.4.0: target for configuration [hunt-console] is up to date.
  Up-to-date hunt-sql 1.6.0: target for configuration [library] is up to date.
  Up-to-date hunt-database 2.3.6: target for configuration [default] is up to date.
  Up-to-date hunt-validation 0.5.0: target for configuration [library] is up to date.
  Up-to-date hunt-entity 2.8.1: target for configuration [library] is up to date.
  Up-to-date hunt-openssl 1.0.5: target for configuration [library] is up to date.
  Up-to-date hunt-jwt 0.2.0-beta.4: target for configuration [library] is up to date.
  Up-to-date hunt-security 0.6.0: target for configuration [library] is up to date.
  Up-to-date hunt-shiro 1.3.1: target for configuration [library] is up to date.
  Up-to-date poodinis 8.1.3: target for configuration [library] is up to date.
  Up-to-date hunt-framework 3.4.6: target for configuration [library] is up to date.
  Up-to-date webapp ~master: target for configuration [application] is up to date.
    Finished To force a rebuild of up-to-date targets, run again with --force
     Running webapp


 ___  ___     ___  ___     ________      _________
|\  \|\  \   |\  \|\  \   |\   ___  \   |\___   ___\     Hunt Framework 3.4.6
\ \  \\\  \  \ \  \\\  \  \ \  \\ \  \  \|___ \  \_|
 \ \   __  \  \ \  \\\  \  \ \  \\ \  \      \ \  \      Listening: 0.0.0.0:8080
  \ \  \ \  \  \ \  \\\  \  \ \  \\ \  \      \ \  \     TLS: Disabled
   \ \__\ \__\  \ \_______\  \ \__\\ \__\      \ \__\
    \|__|\|__|   \|_______|   \|__| \|__|       \|__|    https://www.huntframework.com


Try to browse http://0.0.0.0:8080
\end{minted}


\begin{minted}{text}
stud@sysrescue:~/projects/webapp/source/app/controller$ ps -FC webapp
UID          PID    PPID  C    SZ   RSS PSR STIME TTY          TIME CMD
stud       18551   18544  0 163131 37192  0 17:25 pts/1    00:00:00 /home/stud/projects/webapp/webapp
\end{minted}

\begin{minted}{bash}
stud@sysrescue:~/projects/webapp/source/app/controller$ curl http://localhost:8080/api/fact/9
{"result":"362880"}
stud@sysrescue:~/projects/webapp/source/app/controller$ curl http://localhost:8080/api/test
{"currtime":"2023-11-07T17:25:59.8807696"}
stud@sysrescue:~/projects/webapp/source/app/controller$ curl http://localhost:8080/api/echo/message-to-test
{"echo":"message-to-test"}
\end{minted}

\begin{minted}{html}
  <!--
$ stud@sysrescue:~/projects/webapp/source/app/controller$ curl http://localhost:8080/api/fact/9e
  -->
<!doctype html>
<html lang="en">
    <meta charset="utf-8">
    <title>404 Not Found</title>
    <meta name="viewport" content="width=device-width, initial-scale=1">
    <style>

        * {
            line-height: 3;
            margin: 0;
        }

        html {
            color: #888;
            display: table;
            font-family: sans-serif;
            height: 100%;
            text-align: center;
            width: 100%;
        }

        body {
            display: table-cell;
            vertical-align: middle;
            margin: 2em auto;
        }

        h1 {
            color: #555;
            font-size: 2em;
            font-weight: 400;
        }

        p {
            margin: 0 auto;
            width: 90%;
        }

    </style>
</head>
<body>
    <h1>404 Not Found</h1>
    <p>Sorry!! Unable to complete your request :(</p>

</body>
</html>
\end{minted}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "body"
%%% End:
